CTL mapping - The added value from segregating correlation

### 2012-01-30 inst/methodPaper/document.tex
CTL, and phenotype -> trait

  Single trait CTL profiles can be obtained by transforming the CTL scores into LOD scores. 
  For this we use a look-up table of scores obtained during 15.000 permutation. We note that for each trait this 
  shows a different distribution. We assess the likelyhood and take the $-log10(P)$ of every CTL score to 
  compare QTL profiles with summarized CTL profiles. A CTL profile show the contribution of each phenotype to 
  the total likelyhood.

>>>>

  Single trait CTL profiles can be obtained by transforming the CTL scores into LOD scores. 
  For this we use permutations obtained during 15.000 permutation. We note that for each trait this 
  shows a different distribution of permutation scores. We assess the likelyhood (per trait) and 
  take the $-log10(P)$ of every CTL score to compare QTL profiles with summarized CTL profiles. A CTL profile show the contribution of each phenotype to 
  the total likelyhood.
